---
title: "Rmd with a lot of features"
author: "Audrey"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    self_contained: false
    lib_dir: libs
    keep_md: true
    code_folding: show
    code_download: true
    toc: true
    toc_float: true
    number_sections: true
---

```{r, setup, include = FALSE}
# https://github.com/rstudio/rmarkdown/issues/1453
# fold_plot and fold_output logical option
hooks = knitr::knit_hooks$get()
hook_foldable = function(type) {
  force(type)
  function(x, options) {
    res = hooks[[type]](x, options)
    if (isFALSE(options[[paste0("fold_", type)]])) return(res)
    paste0(
      "<details><summary>", "show", "</summary>\n\n",
      res,
      "\n\n</details>"
    )
  }
}
knitr::knit_hooks$set(
  output = hook_foldable("output"),
  plot = hook_foldable("plot"),
  time_it = local({
    now = NULL
    function(before, options) {
      if (options$time_it) {
        if (before) {
          now <<- Sys.time()
        } else {
          res = difftime(Sys.time(), now, units = "secs")
          paste("(Time to run :", round(res, digits = 2), "s)")
        }
      }
    }
  })
)

own_name = knitr::current_input() # myFileName.Rmd
own_name = substr(own_name, start = 1, stop = nchar(own_name) - 4)
file_dir = paste0("files/", own_name, "_",
                  rawToChar(as.raw(sample(c(48:57,65:90,97:122), 10, replace = TRUE))), "/")

set.seed(1337L)
knitr::opts_chunk$set(echo = TRUE,
                      comment = NA,
                      fig.path = file_dir,
                      
                      # display chunk output
                      message = FALSE,
                      warning = FALSE,
                      fold_output = FALSE, # usefull for sessionInfo()
                      fold_plot = FALSE,
                      
                      # figure settings
                      fig.align = 'center',
                      fig.width = 20,
                      fig.height = 15,
                      
                      # something about seed, chunk and Rmarkdown compilation
                      # https://stackoverflow.com/questions/39417003/long-vectors-not-supported-yet-error-in-rmd-but-not-in-r-script
                      # cache = TRUE,
                      cache.lazy = FALSE, 
                      
                      # add runtime after chunk
                      time_it = FALSE)
```

# Context

## In YML

In `html_document` options, there are :

- toc : there is a table of contents
- toc_float : toc is floating
- number_sections : section are numbered
- code folding : use `class.source = "fold-hide"` to hide code chunk, or `class.source = "fold-show"` to show
- code download : top right button to download the Rmd

## In Rmd

There are hooks in Rmd :

- `fold_output` can be set to `TRUE` or `FALSE`. If `TRUE`, there is a `show` button to show / hide a chunk output
- `fold_plot` can be set to `TRUE` or `FALSE`. If `TRUE`, there is a `show` button to show / hide a chunk plot
- `time_it` can be set to `TRUE` or `FALSE`. If `TRUE`, there is a little text after a chunk to know how many seconds it took to run

# Examples

## time_it

```{r, time_it = TRUE}
Sys.sleep(3)
```

## fold_output

```{r, fold_output = TRUE}
data("mtcars")
head(mtcars)
```

## fold_plot

```{r, fold_plot = TRUE}
plot(mtcars)
```

## fold chunk

```{r, class.source = "fold-hide"}
toto = "Hello world"
print(toto)
```




